The following are papers that have used VLSP for architectural
concepts, as an experimental platform, or both.

\begin{enumerate}
\item

\textbf{Information Exchange Management as a Service for Network Function Virtualization Environments}
\emph{L. Mamatas. S. Clayman. A. Galis}
IEEE Transactions on Network and Service Management – (IEEE TNSM). August 2016.

  \item
\textbf{A Flexible Information Service for Management of Virtualized Software-Defined Infrastructures}
\emph{L. Mamatas, S. Clayman, and A. Galis}
Int. J. Network Mgmt, 26: 396–418. July 2016

  \item
\textbf{Experimenting with Control Operations in Software-Defined Infrastructures}
\emph{S. Clayman. L. Mamatas. A. Galis}
IEEE Network Softwarization (IEEE NetSoft 2016); 6-10 June 2016. 

  \item
\textbf{Efficient Management Solutions for Software Defined Infrastructures}
\emph{S. Clayman. L. Mamatas. A. Galis}
IEEE Network Operations and Management Symposium (NOMS) – 25-29 April 2016. Istanbul.

  \item
\textbf{Energy-efficiency Enablers and Operations in Software-Defined Environments}
\emph{S. Clayman. L. Mamatas. A. Galis}
Management of 5G Networks Workshop at IEEE NOMS 2016. 25-29 April 2016. Istanbul. Turkey

  \item
\textbf{A Service-Aware Virtualized Software-Defined Infrastructure}
\emph{Lefteris Mamatas, Stuart Clayman, Alex Galis}
IEEE Communications Magazine Vol. 53 No. 4 Pg. 166-174, 2015

  \item
\textbf{The Dynamic Placement of Virtual Network Functions}
\emph{Stuart Clayman, Elisa Maini, Alex Galis, Antonio Manzalini, Nicola Mazzocca}
SDNMO, NOMS 2014, Krakow, Poland


%%   \item
%% \textbf{Towards Autonomic Management of Software Enabled Networks}
%% \emph{A. Galis, S. Clayman, & L. Mamatas}
%% 8th International Symposium On Advanced Topics In Electrical Engineering (ATEE), 2013

  \item
\textbf{Management of Software Driven Networks - Research Challenges}
\emph{A. Galis, S. Clayman}
Position Paper, IEEE Intelligent Networking and Collaborative Systems (INCoS 2012), Bucharest, 19-21 September 2012

  \item
\textbf{Selection of Management/Monitoring Nodes in Highly Dynamic Networks}
\emph{R.G. Clegg, S. Clayman, L. Mamatas, G. Pavlou, A. Galis}
IEEE Transactions on Computers, March 2012, IEEE Computer Society Digital Library, IEEE Computer Society

  \item
\textbf{Monitoring, Aggregation and Filtering for Efficient Management of Virtual Networks}
\emph{S. Clayman, R.G. Clegg, L. Mamatas, G. Pavlou, A. Galis}
7th International Conference on Network and Service Management (CNSM), 2011, Paris, Oct 2011
\end{enumerate}
